### 2015-02-26 paper/paper.tex
change directory structure

>>>>

\subsubsection{Negation}

Say we have a rule that inforces agreement: if token at n-1 is Sg,
choose Sg for n as well.

\begin{lstlisting}
rmPlIfSg = Remove [Pl] (C (Exactly -1) [Sg])
rmSgIfPl = Remove [Sg] (C (Exactly -1) [Pl])
\end{lstlisting}

We could also express the rules like this:
\begin{lstlisting}
rmPlIfSg = Remove [Pl] (NOT (C (Exactly (-1)) [Pl]))
rmSgIfPl = Remove [Sg] (NOT (C (Exactly (-1)) [Sg]))
\end{lstlisting}

Although, this is bad: 
\begin{lstlisting}
((1,[Lem "the",Det]),Var 1)
((2,[Lem "bear",N,Sg]),Var 2)
((2,[Lem "bear",V,Pl]),Var 3)
((3,[Lem "sleep",N,Pl]),Var 4)
((3,[Lem "sleep",V,Sg,P3]),Var 5)
\end{lstlisting}

Negation removes both readings for token 2 ``bear'', because the first
token doesn't have any number reading.
